LSTM for Sentiment Analysis on Twitter

### 2015-12-20 paper/paper.tex
add the 'in this paper' part of the intro

% the structure of the paper

>>>>

% the structure of the paper
This paper is laid out as follows: in Section 2, we describe prior work on sentiment classification using deep learning. In Section 3, we describe the structure of our model. In Section 4, we describe the datasets used to train and evaluate our model, as well as results from several experiments. We conclude with an analysis of our results, as well as describe areas of future research.
